Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-04 docs/ms.tex
Update ms.tex

@@

In summary,We have presented a conceptually hierachical inference
approach for weak lensing shear estimation, with carefully calculated 
uncertainty estimates.This method is intrinsically cope with high noise
levels on the input data and naturally allows bad fit to be identified 
from the residuals map. We also have proposed a flexible non-parametric model 
for intrinsic shape distribution allows us to obtain the correct posterior 
distributions, while avoiding making any unsupported assumptions.The Gibbs
sampler allows us to sample the posterior distribution of shear in large number of
sky patches simultaneously and efficiently.
\begin{itemize}
\item We ...
\item The ...
\item The ...
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The probability distribution can be visualised by plotting points at each sample
position. An example in the x, y plane is shown for the posterior distribution of
$\vec{g}$ of 64 sky patches in Fig. .8 galaxy shape profiles in each patch is used as the data.
The number density of samples is proportional to the probability density.The figure shows that the two parameters of $\vec{g}$
do not have strong correlation,since the shape of smaples is close to a circle.
We also shows the histogram of g1 in a single sky patch.Not surprisingly it is close to a Gaussian distribution.
If the probability distribution of parameters are perfect Gaussian,their most probable estimates and uncertainty 
is just the mean and standard deviation of the Gaussian distribution.

@@

In summary,We have presented a conceptually hierachical inference
approach for weak lensing shear estimation, with carefully calculated 
uncertainty estimates.This method is intrinsically cope with high noise
levels on the input data and naturally allows bad fit to be identified 
from the residuals map. We also have proposed a flexible non-parametric model 
for intrinsic shape distribution allows us to obtain the correct posterior 
distributions, while avoiding making any unsupported assumptions.The Gibbs
sampler allows us to sample the posterior distribution of shear in large number of
sky patches simultaneously and efficiently.

Several  model fitting galaxy shape measurent method have been proposed in recent years.
Unlike the average method which merely request a point estimator of galaxy ellipcity,our hierachical bayesian
utilizes the whole likelihood of the galaxy ellipticity.
\begin{itemize}
\item We ...
\item The ...
\item The ...
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
